---
title: "Introduction to StatComp20054"
author: "Xin Liu"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  html_document:
    df_print: paged
vignette: |
  %\VignetteIndexEntry{Introduction to StatComp20054} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

## Overview
__StatComp20054__ is a simple R package, which contains two functions.The purpose is to use the R language package circlize and RIdeogram to visualize the blast double sequence alignment results. One of the _blast_RIdeogram_ for R is to use the R language package Rideogram to display the results of blast double sequence alignment.
RIdeogram is an R language package used to display the idiogram, such as the density distribution of snp; the distribution of a certain type of gene on the chromosome, and so on.
The other is the _blast_circlize_ for R. The circlize package is very powerful, and it is very convenient to draw circles in the R language.So use the circlize package to draw a circle graph to show the results of the blast double sequence alignment

1.use the RIdeogram package for blast sequence alignment:
The data to be prepared is two data frames.
The first is basic information about the genome, including
```{r}
library(RIdeogram)#
head(karyotype_dual_comparison)
```
The second is the result of collinearity analysis
```{r}
head(synteny_dual_comparison)
```

Understand the basic data input format, then we can convert the blast comparison result into this form and run it to get the result:

```{r}
blast_RIdeogram <- function(df1,df2){
library(RIdeogram)#
library(magrittr)
suppressPackageStartupMessages(library("dplyr"))
library("rsvg")
df3<-df2[,c(3,7,8,9,10)]
df3$fill<-ifelse(df3$V3>90,"0080cc",
                 ifelse(df3$V3<80,"0ab276","e64e60"))
df3$Species_1<-1
df3$Species_2<-1
df4 <- df3 %>%
  select(Species_1,V7,V8,Species_2,V9,V10,fill)
colnames(df4)<-colnames(synteny_dual_comparison)
ideogram(karyotype =df1 ,
         synteny=df4,output = "blast_RIdeogram.svg")
rsvg_pdf("blast_RIdeogram.svg","blast_RIdeogram.pdf")
}
```

```{r}
df1<-read.csv("df1.txt",stringsAsFactors = F)
df2<-read.csv("output6.txt",header=F,sep=" ",stringsAsFactors = F)
blast_RIdeogram(df1,df2) 
```


2.Use the R language package circlize to visualize the blast double sequence alignment results

Prepare the data to draw the outermost circle to show the part of the two sequences: df
```{r}
df<-data.frame(chr=c(rep("chloroplast",2),rep("mitochondrial",2)),
               x=c(1,131478,1,444567),
               y=c(0,1,0,1))

df
```
Then read the output of blast: df1

```{r}
df1<-read.csv("output6.txt",stringsAsFactors = F,header=F,sep=" ")
df1
```

Drawing:

```{r}
blast_circlize <- function(df,df1){
suppressPackageStartupMessages(library(circlize))#RIdeogram,magrittr,dplyr,rsvg,circlize,RColorBrewer,ComplexHeatmap
library(RColorBrewer)
suppressPackageStartupMessages(library(ComplexHeatmap))
col<-RColorBrewer::brewer.pal(6,"Paired")
circos.par("start.degree" = 130)
circos.initialize(factors = df$chr,x=df$x)
circos.trackPlotRegion(factors = df$chr,y=df$y,
                       panel.fun = function(x,y){
                         circos.axis()
                       },track.height = 0.1)
highlight.sector(sector.index = "chloroplast",col=col[1])
highlight.sector(sector.index = "mitochondrial",col=col[2])
circos.text(x=70000,y=0.5,
            labels = "chloroplast",
            sector.index = "chloroplast")
circos.text(x=220000,y=0.5,
            labels = "mitochondrial",
            sector.index = "mitochondrial",
            facing = "outside")
col_fun = colorRamp2(c(70,90,100),
                     c("green", "yellow", "red"))
for (i in 1:13){
  x<-sort(c(df1[i,8],df1[i,7]))
  y<-sort(c(df1[i,10],df1[i,9]))
  z<-df1[i,3]
  circos.link("chloroplast",x,"mitochondrial",y,
              col=add_transparency(col_fun(z)))
}
circos.clear()
lgd_links = Legend(at = c(70, 80, 90, 100), 
                   col_fun = col_fun, 
                   title_position = "topleft",
                   title = "identity(%)")
lgd_list_vertical = packLegend(lgd_links)

draw(lgd_list_vertical, x = unit(10, "mm"), 
     y = unit(10, "mm"), just = c("left", "bottom"))
}
```

```{r}
blast_circlize(df,df1)
```




